Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2019-03-08 article.tex
Start of discussion

@@

@@

Thanks to Geert van den Bogaart for his help \richel{reword}.
We thank the Netherlands 
Organization for Scientific Research (NWO) for financial support 
through a VICI grant awarded to RSE.

@@

RJCB, FB and RSE conceived the idea for this research. 
RJCB wrote the code.
FB supplied the DNA alignment.
RJCB, FB and RSE contributed to writing the article.

>>>>

We conclude that MHC-II binds to TMH peptides with a higher/lower/equal
probability than expected by chance.

We conclude that the evolutionary conservation if the TMH parts of membrane
proteins is higher/less/equal compare to its non-TMH counterparts.

@@

We compared the mutation rates between the TMH and non-TMH part of
multiple mycoplasma species. Where we expect no variation 
in mutation rate for every TMH amino acid,
\richel{
  we can test this, but unsure if that would make sense
}
we know that non-TMH part will have regions of different evolutionary
conservation: functional domains, especially in protein-protein
interactions will be strongly conserved, due to an even more constrained
set of peptides that enable a certain function.

@@

Thanks to Geert van den Bogaart for his help \richel{reword}.
Thanks to Maxim for his help \richel{reword}.
We thank the Netherlands 
Organization for Scientific Research (NWO) for financial support 
through a VICI grant awarded to RSE.

@@

RJCB and FB conceived the idea for this research. 
RJCB wrote the code.
FB supplied the DNA alignment.
RJCB, FB and RSE contributed to writing the article.
